---
title: "Overoptimistic predictions and well-calibrated expectations"
subtitle: "Children say they will achieve unrealistic outcomes but are surprised when they do"
author: "Adani B. Abutto, Misha O'Keeffe, Hyowon Gweon"
date: "`r Sys.Date()`"

output:
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cosmo
    highlight: tango

header-includes:
    - \usepackage{setspace}\doublespacing
---

```{r setup, include = F, message = F, warning = F}

## load relevant libraries and functions
require(knitr)         # for knitting
library(DT)            # for datatable() function
library(ordinal)       # for regression
library(Hmisc)         # for bootstrapped confidence intervals
library(ggeffects)     # for logistic regression outputs
library(effectsize)    # for effect sizes
library(png)           # for working with images
library(grid)
library(gganimate)
library(gifski)
library(patchwork)     # for multiple plots
library(tidyverse)     # for everything else
library(ggpubr)
library(dplyr)

## set default code chunk options
knitr::opts_chunk$set(echo = T, warning = F, message = F)

## set default plot theme 
theme_set(theme_classic() + 
            theme(text = element_text(size = 18))) 

plotcolors <- c("#636363", "#0C7BDC")

## fix print width for knitted doc
options(width = 70)

## suppress warnings about grouping 
options(dplyr.summarise.inform = F)
options(xtable.floating = F)
options(xtable.timestamp = "")

## set random seed
set.seed(1)

## set directories for plots and data outputs
figures_dir = '../../figures/'
data_dir = '../../data/'
```

# Data Import

Task data for chance-based game:

```{r}

df.chance_raw =
  as_tibble(read_csv(paste0(data_dir, "chance/chance_data.csv")))

```

Distraction data for chance-based game:

```{r}

df.chance_distraction =
  as_tibble(read_csv(paste0(data_dir, "chance/chance_distraction_data.csv")))  

df.chance_distraction =
  df.chance_distraction %>%
  dplyr::select(subject_id = participant, `Final decision`)

```

Task data for memory game:

```{r}

df.memory_raw =
  as_tibble(read_csv(paste0(data_dir, "memory/memory_data.csv")))

```

Distraction data for memory game:

```{r}

df.memory_distraction =
  as_tibble(read_csv(paste0(data_dir, "memory/memory_distraction_data.csv")))  

df.memory_distraction =
  df.memory_distraction %>%
  dplyr::select(subject_id = participant, `Final decision`)

```


# Data Cleaning

Chance-based task:

```{r}

df.chance =
  df.chance_raw %>%
    # mutate column values
    mutate(
      # rename conditions
      condition = case_when(condition ==
                              "surprising" ~ "Uncued",
                            condition ==
                              "unsurprising" ~ "Cued"),
      # create age bin variable
      age_bin = case_when(age_years < 5.00 ~ 4,
                             age_years >= 5.00 ~ 5),
      # convert gender to numeric (1 is female)
      gender = case_when(child_gender == "f" ~ 1,
                         child_gender == "m" ~ 0),
      # use participant as subject ID
      subject_id = participant,
      # evaluate attention check questions (correct = 1)
      controlq = case_when(attention_check_1 == "correct" ~ 1,
                           attention_check_1 == "incorrect" ~ 0),
      # convert surprise scale to numeric/ordinal
      surprise_binary = case_when(surprise_binary == "not_surprised" ~ 0,
                                  surprise_binary == "surprised" ~ 1),
      # convert surprise scale to numeric/ordinal
      surprise_likert = case_when(surprise_likert == "very_surprised" ~ 3,
                                  surprise_likert == "pretty_surprised" ~ 2,
                                  surprise_likert == "a_little_surprised" ~ 1,
                                  surprise_binary == "0" ~ 0),
      # add version information
      version = "Within-Subject",
      game = "Chance-Based") %>%
    # convert relevant cols to factor format
    mutate(
      # convert surprise scale to numeric/ordinal
      surprise_binary = factor(surprise_binary,
                                    levels = c(0, 1),
                                    labels = c("Not surprised",
                                               "Surprised"),
                                    ordered = T),
      surprise_likert = factor(surprise_likert,
                                    levels = c(0, 1, 2, 3),
                                    labels = c("Not surprised",
                                               "A little surprised",
                                               "Pretty surprised",
                                               "Very surprised"),
                             ordered = T),
           prediction = factor(prediction,
                               levels = c(0, 1, 2, 3),
                               ordered = T),
           condition = factor(condition)) %>%
    # select & rename the final columns
    dplyr::select(subject_id,
           game,
           version,
           completed,
           age_days = child_age,
           age_years,
           age_bin,
           gender,
           condition,
           flipped,
           controlq,
           no_marked_cards = no_marked_cards_chosen,
           surprise_binary,
           surprise_likert,
           prediction)


# add distraction information
df.chance =
  df.chance %>%
  left_join(
    df.chance_distraction %>% select(subject_id, exclusion = `Final decision`),
    by = "subject_id") %>%
  # add column describing hypothesis alignment
  mutate(hypothesis_alignment =
           case_when(condition == "Uncued" &
                       surprise_binary == "Surprised" ~
                       "aligned",
                     condition == "Cued" &
                       surprise_binary == "Not surprised" ~
                       "aligned",
                     condition == "Uncued" &
                       surprise_binary == "Not surprised" ~
                       "against",
                     condition == "Cued" &
                       surprise_binary == "Surprised" ~
                       "against"))

```

Memory task:

```{r}

df.memory =
  df.memory_raw %>%
    # mutate column values
    mutate(
      # rename conditions
      condition = case_when(condition ==
                              "surprising" ~ "Uncued",
                            condition ==
                              "unsurprising" ~ "Cued"),
      # convert gender to numeric (1 is female)
      gender = case_when(child_gender == "f" ~ 1,
                         child_gender == "m" ~ 0),
      # create age bin variable
      age_bin = case_when(age_years < 5.00 ~ 4,
                             age_years >= 5.00 ~ 5),
      # use participant as subject ID
      subject_id = participant,
      # evaluate attention check questions (correct = 1)
      controlq = case_when(attention_check == "correct" ~ 1,
                           attention_check == "incorrect" ~ 0),
      # convert binary surprise to numeric/ordinal
      surprise_binary =
        case_when(surprise_binary == "not_surprised" ~ 0,
                  surprise_binary == "surprised" ~ 1),
      # convert graded surprise to numeric/ordinal
      surprise_likert =
        case_when(surprise_likert == "very_surprised" ~ 3,
                  surprise_likert == "pretty_surprised" ~ 2,
                  surprise_likert == "a_little_surprised" ~ 1,
                  surprise_binary == 0 ~ 0),
      # add version information
      version = "Within-Subject",
      game = "Memory") %>%
    # convert relevant cols to factor format
    mutate(surprise_binary = factor(surprise_binary,
                                    levels = c(0, 1),
                                    labels = c("Not surprised",
                                               "Surprised"),
                                    ordered = T),
           surprise_likert = factor(surprise_likert,
                                    levels = c(0, 1, 2, 3),
                                    labels = c("Not surprised",
                                               "A little surprised",
                                               "Pretty surprised",
                                               "Very surprised"),
                                    ordered = T),
           prediction = factor(prediction,
                               levels = c(0, 1, 2, 3),
                               ordered = T),
           condition = factor(condition),
           # counterbalancing = factor(counterbalancing)
           ) %>%
    # select & rename the final columns
    select(subject_id,
           game,
           version,
           completed,
           age_years,
           age_bin,
           gender,
           condition,
           flipped,
           controlq,
           first_choice, first_choice_dist,
           second_choice, second_choice_dist,
           third_choice, third_choice_dist,
           n_star_cards_selected,
           surprise_binary,
           surprise_likert,
           prediction)

# add distraction information
df.memory =
  df.memory %>%
  left_join(
    df.memory_distraction %>% select(subject_id, exclusion = `Final decision`),
    by = "subject_id") %>%
  # add column describing hypothesis alignment
  mutate(hypothesis_alignment =
           case_when(condition == "Uncued" &
                       surprise_binary == "Surprised" ~
                       "aligned",
                     condition == "Cued" &
                       surprise_binary == "Not surprised" ~
                       "aligned",
                     condition == "Uncued" &
                       surprise_binary == "Not surprised" ~
                       "against",
                     condition == "Cued" &
                       surprise_binary == "Surprised" ~
                       "against"))

```

# Exclusions

## Attention check responses

Chance-based:

```{r}

# attention check question (which cards will you try to find? cards with a star like this, or cards without a star, like this?)
df.chance %>%
  group_by(condition) %>%
  count(condition, controlq)
  
# number of marked cards picked (in "Expected Success" condition, did children pick all 3 cards with the marker on the back?)
df.chance %>%
  group_by(condition) %>%
  filter(condition == "Cued") %>%
  count(condition, no_marked_cards)

```

Memory:

```{r}

# attention check question (which cards will you try to find? cards with a star like this, or cards without a star, like this?)
df.memory %>%
  group_by(condition) %>%
  count(condition, controlq)
  
# number of marked cards picked (in "Expected Success" condition, did children pick all 3 cards with the marker on the back?)
df.memory %>%
  group_by(condition) %>%
  filter(condition == "Cued") %>%
  count(condition, n_star_cards_selected)

```

## Filtering

Exclusions for chance-based game (n = 22)

```{r}

df.chance_analysis =
  df.chance %>%
  # exclude incomplete sessions (n = 6)
  filter(completed == T) %>%
  # exclude children who chose fewer than 3 marked cards in unsurprising (n = 5)
  filter(!(condition == "Cued" & no_marked_cards != 3))

table(df.chance_analysis$exclusion,
      df.chance_analysis$hypothesis_alignment)

```

```{r}

df.chance_analysis =
  df.chance_analysis %>%
  # exclude distracted children as identified via LookIt videos (n = 12) (cf. https://docs.google.com/spreadsheets/d/199JbqM0qQfbuu_J_h6qxV3ffTw6Ode_ccKoyfnNW8Z8/edit?gid=0#gid=0)
  filter(exclusion != "Exclude")

```

Exclusions for memory game (n = 17+19 = 36)

```{r}

df.memory_analysis =
  df.memory %>%
  # filter participants too young (under 4; n = 1)
  filter(age_years > 4.00) %>%
  # exclude incomplete sessions (n = 4)
  filter(completed == T) %>%
  # exclude wrong control q answers (n = 7)
  filter(controlq == 1) %>%
  # exclude 'Expected Success' participants who chose fewer than 3 marked cards (n = 5)
  filter(!(condition == "Cued" &
             n_star_cards_selected != 3))

table(df.memory_analysis$exclusion,
      df.memory_analysis$hypothesis_alignment)

```

```{r}

# n = 21

df.memory_analysis =
  df.memory_analysis %>%
  # exclude distracted children as identified via LookIt videos (cf. https://docs.google.com/spreadsheets/d/1KdfXJgIPxcaOnFA-nAO5pHnJpJyVNks2Pt8U7tTYdoc/edit?gid=0#gid=0)
  filter(exclusion != "Exclude")

```

Exclude excess children in Cued (n = 5):

```{r}

df.memory_analysis =
  df.memory_analysis %>%
  arrange(desc(subject_id)) %>%
  group_by(condition) %>%
  mutate(remove_flag = row_number() <= 5 &
           condition == "Cued") %>%
  ungroup() %>%
  filter(!remove_flag) %>%
  select(-remove_flag)

```

# Descriptives

## Child Demographics

Chance-based game:

```{r}

min(df.chance_analysis$age_years)
max(df.chance_analysis$age_years)

df.chance_analysis %>%
  # group_by(condition) %>%
  summarise(n = n(),
            age = mean(age_years, na.rm = T),
            sd_age = sd(age_years, na.rm = T),
            # 1 is female
            gender = mean(gender, na.rm = T)) %>%
  mutate(across(.cols = where(~ is.numeric(.)),
                .fns = ~ round(., digits = 2))) %>%
  datatable()

```

```{r}

df.chance_analysis %>%
  group_by(condition, age_bin) %>%
  count()

```

Memory game:

```{r}

min(df.memory_analysis$age_years)
max(df.memory_analysis$age_years)

df.memory_analysis %>%
  # group_by(condition) %>%
  summarise(n = n(),
            age = mean(age_years, na.rm = T),
            sd_age = sd(age_years, na.rm = T),
            # 1 is female
            gender = mean(gender, na.rm = T)) %>%
  mutate(across(.cols = where(~ is.numeric(.)),
                .fns = ~ round(., digits = 2))) %>%
  datatable()

```

```{r}

df.memory_analysis %>%
  group_by(condition, age_bin) %>%
  count()

```

# Counterbalancing checks

Chance-based:

```{r}

df.chance_analysis %>%
  count(flipped, condition)

```

```{r}

# flipped not logged in chance protocol — counterbalancing regressions n/a
# summary(clm(prediction ~ 1 + flipped,
#             data = df.chance_analysis))
#
# summary(clm(surprise_binary ~ 1 + flipped,
#             data = df.chance_analysis))
#
# summary(clm(surprise_likert ~ 1 + flipped,
#             data = df.chance_analysis))

```

Memory:

```{r}

df.memory_analysis %>%
  count(flipped, condition)

```

```{r}

# regression
summary(clm(prediction ~ 1 + flipped,
            data = df.memory_analysis))

summary(clm(surprise_binary ~ 1 + flipped,
            data = df.memory_analysis))

summary(clm(surprise_likert ~ 1 + flipped,
            data = df.memory_analysis))

```

```{r fig.width = 21, fig.height = 12}

df.memory_analysis %>%
    ggplot(aes(x = flipped,
           y = as.numeric(surprise_likert),
           fill = flipped,
           group = flipped,
           color = flipped)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Counterbalancing",
                    labels = c("'Not Surprised' First",
                               "'Surprised' First"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("Not (0)", "A little (1)","Pretty (2)", "Very (3)")) +
  labs(
    subtitle = "How surprised are you?",
    y = "Surprise response",
    x = "Response order flipped?") +
  theme_classic(base_size = 50) +
  theme(legend.position = "none",
        axis.ticks.length = unit(0.05, "cm"),
        panel.spacing = unit(0.01, "lines"))

```

# Figures

## Chance-Based

### Prediction

```{r fig.width = 21, fig.height = 12}

plot.chance_prediction =
  df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(prediction),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
    geom_segment(
    x = 1.75, xend = 2.25,   
    y = 1.6, yend = 1.6,
    linetype = "dashed",
    color = "#0C7BDC",
    linewidth = 2
  ) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("0 stars", "1 star","2 stars", "3 stars")) +
  labs(
       subtitle = "Do you think you'll get no stars, 1 star, 2 stars, or 3 stars?",
       y = "Prediction",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines"))

plot.chance_prediction

# ggsave((paste0(figures_dir, "chance/chance_prediction.png")),
#        plot = plot.chance_prediction,
#        width = 21, height = 12, device = "png")

```

By age:

```{r fig.width = 30, fig.height = 12}

df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(prediction),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
    geom_segment(
    x = 1.75, xend = 2.25,   
    y = 1.6, yend = 1.6,
    linetype = "dashed",
    color = "#0C7BDC",
    linewidth = 2
  ) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("0 stars", "1 star","2 stars", "3 stars")) +
  labs(
       subtitle = "Do you think you'll get no stars, 1 star, 2 stars, or 3 stars?",
       y = "Prediction",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines")) +
  facet_wrap(~age_bin)

```

### Binary Surprise

```{r fig.width = 21, fig.height = 12}

plot.chance_binary =
  df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_binary),
           fill = condition,
           group = condition,
           color = condition)) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = .5,
               binwidth = .1,
               color = "black") +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1, 2),
                     labels = c("No (0)","Yes (1)")) +
  labs(
       subtitle = "Are you surprised, or are you not surprised?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
  theme(legend.position = "none",
        axis.ticks.length = unit(0.05, "cm"),
        panel.spacing = unit(0.01, "lines"))

plot.chance_binary

# ggsave((paste0(figures_dir, "chance/chance_binary_surprise.png")),
#        plot = plot.chance_binary,
#        width = 20, height = 12, device = "png")

```

By age:

```{r fig.width = 30, fig.height = 12}

df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_binary),
           fill = condition,
           group = condition,
           color = condition)) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           color = "black",
           linewidth = 2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = .5,
               binwidth = .1,
               color = "black") +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1, 2),
                     labels = c("No (0)","Yes (1)")) +
  labs(
       subtitle = "Are you surprised, or are you not surprised?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
  theme(legend.position = "none",
        axis.ticks.length = unit(0.05, "cm"),
        panel.spacing = unit(0.01, "lines")) +
    facet_wrap(~age_bin)

```

### Graded Surprise

```{r fig.width = 20, fig.height = 12}

plot.chance_graded =
  df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_likert),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("Not (0)", "A little (1)","Pretty (2)", "Very (3)")) +
  labs(
       subtitle = "How surprised are you?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines"))

plot.chance_graded

# ggsave((paste0(figures_dir, "chance/chance_graded_surprise.png")),
#        plot = plot.chance_graded,
#        width = 20, height = 12, device = "png")

```

By age:

```{r fig.width = 30, fig.height = 12}

df.chance_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_likert),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("Not (0)", "A little (1)","Pretty (2)", "Very (3)")) +
  labs(
       subtitle = "How surprised are you?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines")) +
    facet_wrap(~age_bin)

```

```{r fig.width = 61, fig.height = 12}

plot.chance_sidebyside =
  plot.chance_prediction +
  plot.chance_binary +
  plot.chance_graded

plot.chance_sidebyside +
  theme(legend.position = "none")

```

## Memory

### Prediction

```{r fig.width = 21, fig.height = 12}

plot.memory_prediction =
  df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(prediction),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_segment(
    x = 1.75, xend = 2.25,   
    y = 1.53, yend = 1.53,
    linetype = "dashed",
    color = "#0C7BDC",
    linewidth = 2
  ) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("0 stars", "1 star","2 stars", "3 stars")) +
  labs(
       subtitle = "Do you think you'll get no stars, 1 star, 2 stars, or 3 stars?",
       y = "Prediction",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines"))

plot.memory_prediction

# ggsave((paste0(figures_dir, "memory/memory_prediction.png")),
#        plot = plot.memory_prediction,
#        width = 21, height = 12, device = "png")

```

By age:

```{r fig.width = 22.5, fig.height = 12}

df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(prediction),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_segment(
    x = 1.75, xend = 2.25,   
    y = 1.53, yend = 1.53,
    linetype = "dashed",
    color = "#0C7BDC",
    linewidth = 2
  ) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("0 stars", "1 star","2 stars", "3 stars")) +
  labs(
       subtitle = "Do you think you'll get no stars, 1 star, 2 stars, or 3 stars?",
       y = "Prediction",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines")) +
  facet_wrap(~age_bin)

# ggsave((paste0(figures_dir, "memory/memory_prediction_age.png")),
#        width = 21, height = 12, device = "png")

```

### Binary Surprise

```{r fig.width = 20, fig.height = 12}

plot.memory_binary =
  df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_binary),
           fill = condition,
           group = condition,
           color = condition)) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 5,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = .5,
               binwidth = .1,
               color = "black") +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1, 2),
                     labels = c("No (0)","Yes (1)")) +
  labs(
       subtitle = "Are you surprised, or are you not surprised?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
  theme(legend.position = "none",
        axis.ticks.length = unit(0.05, "cm"),
        panel.spacing = unit(0.01, "lines"))

plot.memory_binary

# ggsave((paste0(figures_dir, "memory/memory_binary_surprise.png")),
#        plot = plot.memory_binary,
#        width = 20, height = 12, device = "png")

```

By age:

```{r fig.width = 21, fig.height = 12}

df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_binary),
           fill = condition,
           group = condition,
           color = condition)) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 5,
           shape = 23,
           color = "black",
           linewidth = 2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = .45,
               binwidth = .1,
               color = "black") +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1, 2),
                     labels = c("No (0)","Yes (1)")) +
  labs(
       subtitle = "Are you surprised, or are you not surprised?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
  theme(legend.position = "none",
        axis.ticks.length = unit(0.05, "cm"),
        panel.spacing = unit(0.01, "lines")) +
  facet_wrap(~age_bin)

# ggsave((paste0(figures_dir, "memory/memory_binary_surprise_age.png")),
#        width = 20, height = 12, device = "png")

```

### Graded Surprise

```{r fig.width = 20, fig.height = 12}

plot.memory_graded =
  df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_likert),
           fill = condition,
           group = condition,
           color = condition)) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1,
               binwidth = .1,
               alpha = 1,
               color = "black") +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 4,
           shape = 23,
           fill = plotcolors,
           color = "black",
           linewidth = 2) +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("Not (0)", "A little (1)","Pretty (2)", "Very (3)")) +
  labs(
       subtitle = "How surprised are you?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines"))

plot.memory_graded

# ggsave((paste0(figures_dir, "memory/memory_graded_surprise.png")),
#        plot = plot.memory_graded,
#        width = 20, height = 12, device = "png")

```

By age:

```{r fig.width = 21, fig.height = 12}

df.memory_analysis %>%
  ggplot(aes(x = condition,
           y = as.numeric(surprise_likert),
           fill = condition,
           group = condition,
           color = condition)) +
  stat_summary(fun.data = "mean_cl_boot",
           geom = "pointrange",
           size = 5,
           shape = 23,
           color = "black",
           linewidth = 2) +
  geom_dotplot(binaxis = "y",
               stackdir = "center",
               dotsize = 1.25,
               binwidth = .1,
               color = "black") +
  scale_fill_manual(name = "Condition",
                    labels = c("Cued",
                               "Uncued"),
                    values = plotcolors) +
  scale_color_manual(values = plotcolors,
                     guide = "none") +
  scale_y_continuous(breaks = c(1:4),
                     labels = c("Not (0)", "A little (1)","Pretty (2)", "Very (3)")) +
  labs(
       subtitle = "How surprised are you?",
       y = "Surprise response",
       x = element_blank()) +
  theme_classic(base_size = 50) +
    theme(legend.position = "none",
      axis.ticks.length = unit(0.05, "cm"),
      panel.spacing = unit(0.01, "lines")) +
  facet_wrap(~age_bin)

# ggsave((paste0(figures_dir, "memory/memory_graded_surprise_age.png")),
#        width = 20, height = 12, device = "png")

```

```{r fig.width = 61, fig.height = 12}

plot.memory_sidebyside =
  plot.memory_prediction +
  plot.memory_binary +
  plot.memory_graded

plot.memory_sidebyside +
  theme(legend.position = "none")

```

------------------------------------------------------------------------------------------

# Inferential Statistics

## Chance-Based Game

### Prediction

Table:

```{r}

df.chance_analysis %>%
  count(condition, prediction)

```

```{r}

df.chance_analysis %>%
  mutate(prediction_numerical =
           case_when(prediction == "0" ~ 0,
                     prediction == "1" ~ 1,
                     prediction == "2" ~ 2,
                     prediction == "3" ~ 3)) %>%
  group_by(condition) %>%
  summarise(mean = mean(prediction_numerical),
            sd = sd(prediction_numerical))

```

```{r}

# The expected value for "Unexpected Success" is .6 because we can approximate each draw’s probability as: \mathbb{P}(\text{sun card}) = \frac{3}{15} = 0.2. Then: \mathbb{E}[X_1] = \mathbb{E}[X_2] = \mathbb{E}[X_3] = 0.2 \Rightarrow \mathbb{E}[X] = 0.2 + 0.2 + 0.2 = \boxed{0.6}

temp =
  df.chance_analysis %>%
  # convert prediction scale values to numeric
  mutate(prediction_numerical =
           case_when(prediction == "0" ~ 0,
                     prediction == "1" ~ 1,
                     prediction == "2" ~ 2,
                     prediction == "3" ~ 3)) %>%
  filter(condition == "Uncued")

# run t-test
t.test(temp$prediction_numerical,
       mu = .6,
       alternative = "two.sided")

```

Between conditions:

```{r}

t.test(as.numeric(prediction) ~ condition,
       alternative = "two.sided",
       data = df.chance_analysis)

```

### Surprise vs Chance

Is rate of surprise sig above 50%?

```{r}

temp =
  df.chance_analysis %>%
  filter(condition == "Uncued") %>%
  mutate(surprise_binary = case_when(surprise_binary == "Surprised" ~ 1,
                                     surprise_binary == "Not surprised" ~ 0))

t.test(as.numeric(temp$surprise_binary),
       mu = .5,
       alternative = "greater")

```

### Binary Surprise

Table:

```{r}

df.chance_analysis %>%
  count(condition, surprise_binary)

```

```{r}

df.chance_analysis %>%
  mutate(surprise_binary_numerical =
           case_when(surprise_binary == "Not surprised" ~ 0,
                     surprise_binary == "Surprised" ~ 1)) %>%
  group_by(condition) %>%
  summarise(mean = mean(surprise_binary_numerical),
            sd = sd(surprise_binary_numerical))

```

Regression:

```{r fig.width = 14, fig.height = 8}

# logistic regression
fit.chance_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.chance_analysis)

# print model outputs
fit.chance_surprise %>%
  summary()

# plot model predictions
probs.chance_surprise =
  ggpredict(fit.chance_surprise)

probs.chance_surprise

plot(probs.chance_surprise) +
  ylim(0, 1) +
  labs(title = "Predicted Probabilities per Surprise Scale Value",
       subtitle = "1 = Not surprised, 2 = Surprised",
       x = "Condition",
       y = "Predicted Probability") +
  theme_classic(base_size = 18)

```

Checking for age interaction:

```{r}

# logistic regression
fit.chance_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
    data = df.chance_analysis)

# print model outputs
fit.chance_surprise %>%
  summary()

```

Wilcox:

```{r}

wilcox.test(as.numeric(surprise_binary) ~ condition,
            data = df.chance_analysis)

```

### Graded Surprise

Table:

```{r}

df.chance_analysis %>%
  count(condition, surprise_likert)

```

```{r}

df.chance_analysis %>%
  mutate(surprise_likert_numerical =
           case_when(surprise_likert == "Not surprised" ~ 0,
                     surprise_likert == "A little surprised" ~ 1,
                     surprise_likert == "Pretty surprised" ~ 2,
                     surprise_likert == "Very surprised" ~ 3)) %>%
  group_by(condition) %>%
  summarise(mean = mean(surprise_likert_numerical),
            sd = sd(surprise_likert_numerical))

```

Regression:

```{r fig.width = 14, fig.height = 8}

# logistic regression
fit.chance_surprise_graded =
  clm(
    # graded surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.chance_analysis)

# print model outputs
fit.chance_surprise_graded %>%
  summary()

# plot model predictions
probs.chance_surprise_graded =
  ggpredict(fit.chance_surprise_graded)

probs.chance_surprise_graded

```

Checking for age interaction:

```{r}

# logistic regression
fit.chance_surprise =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
    data = df.chance_analysis)

# print model outputs
fit.chance_surprise %>%
  summary()

```

Wilcox:

```{r}

wilcox.test(as.numeric(surprise_likert) ~ condition,
            data = df.chance_analysis)

```

### Robustness Tests

Correlation:

```{r}

cor.test(as.numeric(df.chance_analysis$prediction),
         as.numeric(df.chance_analysis$surprise_likert),
         method = "spearman")

```

```{r fig.width = 9, fig.height = 6}

plot.correlation =
  df.chance_analysis %>%
  ggplot(aes(x = prediction,
             y = surprise_likert)) +
  geom_dotplot(dotsize = .7,
               binaxis = "y",
               stackdir = "center",
               stackratio = 1,
               color = "black",
               fill = "lightblue") +
  # geom_point(size = 3,
  #            color = "black",
  #            position = position_jitter(width = .075,
  #                                       height = 0),
  #            alpha = .2) +
  labs(x = "A Priori Prediction",
       y = "Post-Hoc Surprise Response")

plot.correlation

# ggsave((paste0(figures_dir, "chance/chance_correlation.png")),
#        plot = plot.correlation,
#        width = 9, height = 6, device = "png")

```

Subsetting for children who predicted 3 stars:

```{r}

df.robust_chance =
  df.chance_analysis %>%
  filter(prediction == 3)

```

```{r}

# logistic regression
fit.chance_surprise =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_chance)

# print model outputs
fit.chance_surprise %>%
  summary()

```

```{r}

# logistic regression
fit.chance_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_chance)

# print model outputs
fit.chance_surprise %>%
  summary()

```

## Memory Game

### Manhattan Distance

Visualization of what Manhattan distance means:

```{r fig.width = 10, fig.height = 8}

draw_manhattan =
  function(n_rows = 5,
           n_cols = 10,
           target_row = 3,
           target_col = 5,
           highlight_dist = 3) {
    grid = expand.grid(row = 1:n_rows, col = 1:n_cols) %>%
      mutate(dist = abs(row - target_row) + abs(col - target_col),
             highlight = dist == highlight_dist)
    
    ggplot(grid, aes(x = col, y = row)) +
      geom_tile(aes(fill = dist), color = "grey85", size = 0.4) +
      geom_tile(data = dplyr::filter(grid, highlight),
                fill = NA, color = "red3", size = 1.2) +
      geom_point(data = data.frame(row = target_row, col = target_col),
                 aes(x = col, y = row), inherit.aes = FALSE,
                 shape = 21, size = 4,
                 fill = "gold", color = "black", stroke = 1.2) +
      geom_text(aes(label = dist), size = 3) +
      scale_fill_gradient(low = "#f0f9e8", high = "#2b8cbe",
                          name = "Manhattan distance") +
      coord_fixed(expand = FALSE) +
      scale_x_continuous(breaks = 1:n_cols, minor_breaks = NULL) +
      scale_y_reverse(breaks = 1:n_rows, minor_breaks = NULL) +
      labs(x = "Column", y = "Row",
           title = paste0(n_rows, "×",
                          n_cols,
                          " grid with Manhattan distance"),
           subtitle = paste0("Target at row ", target_row, ", column ", target_col, " (red outline = distance ", highlight_dist, ")")) +
      theme(legend.position = "right",
            panel.border = element_rect(color = "black", fill = NA))
    }

# plot with 5x10 grid
draw_manhattan(5, 10,
               target_row = 3,
               target_col = 5,
               highlight_dist = 3)

```

```{r}

df.memory_analysis =
  df.memory_analysis %>% 
  # compute mean value
  mutate(mean_manhattan_distance =
           case_when(condition == "Uncued" ~
                       (first_choice_dist +
                          second_choice_dist +
                          third_choice_dist)/3,
                     condition == "unsurprising" ~ NA))

```

Performance across trials:

```{r}

df.memory_analysis %>%
  filter(condition == "Uncued") %>%
  count(n_star_cards_selected)

```

```{r}

df.memory_analysis %>%
  filter(condition == "Uncued") %>%
  count(first_choice_dist)

```

```{r}

df.memory_analysis %>%
  filter(condition == "Uncued") %>%
  count(second_choice_dist)

```

```{r}

df.memory_analysis %>%
  filter(condition == "Uncued") %>%
  count(third_choice_dist)

```

```{r}

df.memory_analysis %>%
  filter(condition == "Uncued") %>% 
  summarise(avg_manhattan_distance = mean(mean_manhattan_distance),
            sd_avg_manhattan_distance = sd(mean_manhattan_distance),
            avg_first_choice_dist = mean(first_choice_dist),
            avg_second_choice_dist = mean(second_choice_dist),
            avg_third_choice_dist = mean(third_choice_dist))

```

Performance by trial:

```{r}

df.distance =
  df.memory_analysis %>%
  pivot_longer(cols = ends_with("_dist"),
               names_to = "choice",
               values_to = "distance") %>%
  mutate(choice = factor(choice,
                         levels = c("first_choice_dist",
                                    "second_choice_dist",
                                    "third_choice_dist"),
                         labels = c("First Trial",
                                    "Second Trial",
                                    "Third Trial")))

```

```{r}

df.distance %>%
  filter(condition == "Uncued") %>%
  group_by(choice) %>%
  summarise(mean = mean(distance, na.rm = T),
            sd = sd(distance, na.rm = T))

summary(lm(distance ~ choice, data = df.distance %>%  filter(condition == "Uncued")))

```

```{r fig.width = 12, fig.height = 7}

ggplot(df.memory_analysis,
       aes(x = mean_manhattan_distance)) +
  geom_histogram(color = "white", bins = 10,
                 fill = "black") +
  labs(x = "Mean manhattan distance across trials",
       y = "# of children",
       title = "Distribution of mean manhattan distance across 3 trials") +
  scale_x_continuous(limits = c(0, 3),
                     breaks = seq(0, 3, by = 0.33)) +
  scale_y_continuous(limits = c(0, 10),
                     breaks = c(seq(0, 10, 1))) +
  theme_classic(base_size = 24)

```

```{r fig.width = 12, fig.height = 7}

df.distance %>%
  filter(condition == "Uncued") %>% 
  ggplot(aes(x = choice, y = distance)) +
  geom_boxplot(width = .15, outlier.shape = NA) +
  geom_jitter(width = .05, height = .02, alpha = .3, size = 4) +
  labs(x = "Choice", y = "Distance to true location (Manhattan)",
       title = "Per-trial distance between participant choice and true location") +
  theme_classic(base_size = 24)

```

```{r fig.width = 14, fig.height = 7}

df.distance %>%
  filter(condition == "Uncued") %>% 
  ggplot(aes(x = choice, y = distance,
             group = subject_id)) +
  geom_line(alpha = 0.3, size = 1, color = "steelblue") +
  geom_jitter(height = 0, width = .05, alpha = 0.3, size = 5) +
  labs(x = "Trial", y = "Manhattan distance",
       title = "WITHIN-PARTICIPANT trajectories:\nDistance between participant choice and true card location across trials") +
    theme_classic(base_size = 24)

```

In "Unexpected Success", does Manhattan Distance negatively correlate with surprise so
that card picks closer to true locations lead to lower levels of reported surprise?

```{r}

temp =
  df.memory_analysis %>% 
  filter(condition == "Uncued")

summary(clm(surprise_binary ~ 1 + mean_manhattan_distance,
            data = temp))

summary(clm(surprise_likert ~ 1 + mean_manhattan_distance,
            data = temp))

```

```{r fig.width = 12, fig.height = 8}

plot.correlation =
  temp %>%
  ggplot(aes(x = mean_manhattan_distance,
             y = surprise_likert)) +
  geom_dotplot(dotsize = .5,
               binaxis = "x",
               stackratio = 1,
               color = "black",
               fill = "lightblue") +
  scale_x_continuous(limits = c(0, 3),
                     breaks = c(seq(0, 3, .333))) +
  labs(x = "Mean Manhattan Distance of Card Picks",
       y = "Post-Hoc Surprise Response")

plot.correlation

# ggsave((paste0(figures_dir, "memory/distance_correlation.png")),
#        plot = plot.correlation,
#        width = 12, height = 8, device = "png")

```

### Prediction

Table:

```{r}

df.memory_analysis %>%
  count(condition, prediction)

```

```{r}

df.memory_analysis %>%
  mutate(prediction_numerical =
           case_when(prediction == "0" ~ 0,
                     prediction == "1" ~ 1,
                     prediction == "2" ~ 2,
                     prediction == "3" ~ 3)) %>%
  group_by(condition) %>%
  summarise(mean = mean(prediction_numerical),
            sd = sd(prediction_numerical))

```

True performance:

```{r}

df.memory_analysis %>%
  count(condition, n_star_cards_selected)

```

```{r}

df.memory_analysis %>%
  group_by(condition) %>%
  summarise(mean = mean(n_star_cards_selected),
            median = median(n_star_cards_selected),
            sd = sd(n_star_cards_selected))

```

Between conditions:

```{r}

t.test(as.numeric(prediction) ~ condition,
       alternative = "two.sided",
       data = df.memory_analysis)

```

Comparison:

```{r}

# Children's true performance is .56.

temp =
  df.memory_analysis %>%
  # convert prediction scale values to numeric
  mutate(prediction_numerical =
           case_when(prediction == "0" ~ 0,
                     prediction == "1" ~ 1,
                     prediction == "2" ~ 2,
                     prediction == "3" ~ 3)) %>%
  filter(condition == "Uncued")

# run t-test
t.test(temp$prediction_numerical,
       mu = mean(temp$n_star_cards_selected),
       alternative = "two.sided")

```

### Surprise vs Chance

```{r}

temp =
  df.memory_analysis %>%
  filter(condition == "Uncued") %>%
  mutate(surprise_binary = case_when(surprise_binary == "Surprised" ~ 1,
                                     surprise_binary == "Not surprised" ~ 0))

t.test(as.numeric(temp$surprise_binary),
       mu = .5,
       alternative = "greater")

```

### Binary Surprise

Table:

```{r}

df.memory_analysis %>%
  count(condition, surprise_binary)

```

```{r}

df.memory_analysis %>%
  mutate(surprise_binary_numerical =
           case_when(surprise_binary == "Not surprised" ~ 0,
                     surprise_binary == "Surprised" ~ 1)) %>%
  group_by(condition) %>%
  summarise(mean = mean(surprise_binary_numerical),
            sd = sd(surprise_binary_numerical))

```

Regression:

```{r fig.width = 14, fig.height = 8}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
      # control for true performance
      # n_star_cards_selected,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise %>%
  summary()

# plot model predictions
probs.memory_surprise =
  ggpredict(fit.memory_surprise)

probs.memory_surprise

plot(probs.memory_surprise) +
  ylim(0, 1) +
  labs(title = "Predicted Probabilities per Surprise Scale Value",
       subtitle = "1 = Not surprised, 2 = Surprised",
       x = "Condition, age_years] ",
       y = "Predicted Probability") +
  theme_classic(base_size = 18)

```

Just age:

```{r}

# logistic regression
summary(
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # age as predictor
      age_bin,
    data = df.memory_analysis)
)

```

Age moderation:

```{r fig.width = 14, fig.height = 8}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
      # control for true performance
      # n_star_cards_selected,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise %>%
  summary()

# plot model predictions
probs.memory_surprise =
  ggpredict(fit.memory_surprise)

plot(probs.memory_surprise)

```

```{r}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition * age_years,
      # control for true performance
      # n_star_cards_selected,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise %>%
  summary()

# plot model predictions
probs.memory_surprise =
  ggpredict(fit.memory_surprise)

plot(probs.memory_surprise)

```

Subsetting for 4s:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
      # control for true performance
      # n_star_cards_selected,
    data = df.memory_analysis %>%
      filter(age_bin == 4))
  )

```

Subsetting for 5s:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
      # control for true performance
      # n_star_cards_selected,
    data = df.memory_analysis %>%
      filter(age_bin == 5))
  )

```

Wilcox:

```{r}

wilcox.test(as.numeric(surprise_binary) ~ condition,
            data = df.memory_analysis)

```

### Graded Surprise

Table:

```{r}

df.memory_analysis %>%
  count(condition, surprise_likert)

```

```{r}

df.memory_analysis %>%
  mutate(surprise_likert_numerical =
           case_when(surprise_likert == "Not surprised" ~ 0,
                     surprise_likert == "A little surprised" ~ 1,
                     surprise_likert == "Pretty surprised" ~ 2,
                     surprise_likert == "Very surprised" ~ 3)) %>%
  group_by(condition) %>%
  summarise(mean = mean(surprise_likert_numerical),
            sd = sd(surprise_likert_numerical))

```

Regression:

```{r fig.width = 14, fig.height = 8}

# logistic regression
fit.memory_surprise_graded =
  clm(
    # graded surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise_graded %>%
  summary()

# plot model predictions
probs.memory_surprise_graded =
  ggpredict(fit.memory_surprise_graded)

probs.memory_surprise_graded

```

Wilcox:

```{r}

wilcox.test(as.numeric(surprise_likert) ~ condition,
            data = df.memory_analysis)

```

Age as sole predictor:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # age as predictor
      age_bin,
    data = df.memory_analysis))

```

Age moderation effect:

```{r}

# logistic regression
fit.memory_surprise_graded =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise_graded %>%
  summary()

# logistic regression
fit.memory_surprise_graded =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition * age_years,
    data = df.memory_analysis)

# print model outputs
fit.memory_surprise_graded %>%
  summary()

```

```{r fig.height = 3, fig.width = 8}

# plot model predictions
probs.memory_surprise =
  ggpredict(fit.memory_surprise_graded,
            terms = c("age_years", "condition"))

plot(probs.memory_surprise,
     n_rows = 1) + 
  scale_y_continuous(limits = c(0, 1),
                     breaks = c(0, .25, .5, .75, 1)) +
  labs(y = "P of endorsing Likert scale value",
       x = "Age in years (cont.)",
       title = "Model output: Predicted probabilities by Likert scale value & age") +
  theme(legend.position = "top")

```

Subsetting for 4s:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.memory_analysis %>%
      filter(age_bin == 4)))

```

Subsetting for 5s:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.memory_analysis %>%
      filter(age_bin == 5))
  )

```

### Robustness Tests

Correlation:

```{r}

cor.test(as.numeric(df.memory_analysis$prediction),
         as.numeric(df.memory_analysis$surprise_likert),
         method = "spearman")

```

```{r fig.width = 9, fig.height = 6}

plot.correlation =
  df.memory_analysis %>%
  ggplot(aes(x = prediction,
             y = surprise_likert)) +
  geom_dotplot(dotsize = .7,
               binaxis = "y",
               stackdir = "center",
               stackratio = 1,
               color = "black",
               fill = "lightblue") +
  # geom_point(size = 3,
  #            color = "black",
  #            position = position_jitter(width = .075,
  #                                       height = 0),
  #            alpha = .2) +
  labs(x = "A Priori Prediction",
       y = "Post-Hoc Surprise Response")

plot.correlation

# ggsave((paste0(figures_dir, "memory/memory_correlation.png")),
#        plot = plot.correlation,
#        width = 9, height = 6, device = "png")

```

Subsetting for children who predicted 3 stars:

```{r}

df.robust_memory =
  df.memory_analysis %>%
  filter(prediction == 3)

```

```{r}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_memory)

# print model outputs
fit.memory_surprise %>%
  summary()

```

```{r}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_memory)

# print model outputs
fit.memory_surprise %>%
  summary()

```

Age effects for subset:

```{r}

df.robust_memory %>%
  group_by(condition, age_bin) %>%
  count()

```

Age as sole predictor:

```{r}

summary(
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # age as predictor
      age_bin,
    data = df.robust_memory)
  )


summary(
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # age as predictor
      age_bin,
    data = df.robust_memory)
  )

```

Moderation:

```{r}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
    data = df.robust_memory)

# print model outputs
fit.memory_surprise %>%
  summary()

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition * age_bin,
    data = df.robust_memory)

# print model outputs
fit.memory_surprise %>%
  summary()

```

Subsetting for 5s:

```{r}

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_binary ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_memory %>%
      filter(age_bin == 5))

# print model outputs
fit.memory_surprise %>%
  summary()

# logistic regression
fit.memory_surprise =
  clm(
    # binary surprise is DV
    surprise_likert ~
      # intercept
      1 +
      # condition as predictor
      condition,
    data = df.robust_memory %>%
      filter(age_bin == 5))

# print model outputs
fit.memory_surprise %>%
  summary()

```

# Non-3 Choosers

Chance-Based:

```{r}

df.chance %>%
  # exclude incomplete sessions
  filter(completed == T) %>%
  # exclude wrong control q answers
  filter(controlq == 1) %>%
  filter(no_marked_cards < 3) %>%
  count(prediction, surprise_binary)

df.chance %>%
  # exclude incomplete sessions
  filter(completed == T) %>%
  # exclude wrong control q answers
  filter(controlq == 1) %>%
  filter(no_marked_cards < 3) %>%
  count(prediction, surprise_likert)

```

Memory:

```{r}

df.memory %>%
  # exclude incomplete sessions
  filter(completed == T) %>%
  # exclude wrong control q answers
  filter(controlq == 1) %>%
  filter(condition == "Cued",
         n_star_cards_selected < 3) %>%
  count(prediction, surprise_binary)

df.memory %>%
  # exclude incomplete sessions
  filter(completed == T) %>%
  # exclude wrong control q answers
  filter(controlq == 1) %>%
  filter(condition == "Cued",
         n_star_cards_selected < 3) %>%
  count(prediction, surprise_likert)

```

# Main Analyses Including Interference/Distraction Kids

*Chance-based*

```{r}

df.qualitative =
  df.chance %>%
  # exclude incomplete sessions (n = 6)
  filter(completed == T) %>%
  # exclude children who chose fewer than 3 marked cards in unsurprising (n = 5)
  filter(!(condition == "Cued" & no_marked_cards != 3))
# but keep kids who were distracted

```

Prediction:

```{r}

df.qualitative %>%
  count(condition, prediction)

```

Binary surprise:

```{r}

summary(
  clm(surprise_binary ~ condition,
      data = df.qualitative %>% 
        filter(prediction == 3))
)

```

Graded surprise:

```{r}

summary(
  clm(surprise_likert ~ condition,
      data = df.qualitative %>%
        filter(prediction == 3))
)

```

*Memory*

```{r}

df.qualitative =
  df.memory %>%
  # filter participants too young (under 4; n = 1)
  filter(age_years > 4.00) %>%
  # exclude incomplete sessions (n = 4)
  filter(completed == T) %>%
  # exclude wrong control q answers (n = 7)
  filter(controlq == 1) %>%
  # exclude 'Expected Success' participants who chose fewer than 3 marked cards (n = 5)
  filter(!(condition == "Cued" &
             n_star_cards_selected != 3))

```

Prediction

```{r}

df.qualitative %>%
  count(condition, prediction)

```

Binary surprise:

```{r}

summary(
  clm(surprise_binary ~ condition,
      data = df.qualitative %>% 
        filter(prediction == 3))
)

summary(
  clm(surprise_binary ~ condition * age_bin,
      data = df.qualitative)
)

```

Graded surprise:

```{r}

summary(
  clm(surprise_likert ~ condition,
      data = df.qualitative %>% 
        filter(prediction == 3))
)

summary(
  clm(surprise_likert ~ condition * age_bin,
      data = df.qualitative)
  )

```
